The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-09-29 src/paper/model/testing.tex
Add some last references.

We solve the first challenge by assuming that the share of detected cases would have
remained at the level it reached before Christmas if rapid tests had not become
available. While this is only an approximation to reality, changes in the share of
detected cases that would have happened without rapid tests are very likely to be small
compared to the changes caused by rapid tests.

@@

In contrast to PCR tests, rapid tests are not perfect and can be falsely positive or
falsely negative. While the specificity of rapid tests is calibrated at 99.4\%
\citep{Bruemmer2021}, their sensitivity strongly depends on the timing of the rapid test
relative to the start of infectiousness \citep{Smith2021}. Before the onset of
infectiousness the sensitivity is very low (35\%). On the first day of infectiousness it
is much higher (88\%) but still lower than during the remaining infectious period (92\%).
After infectiousness stops, the sensitivity drops to 50 \%.

>>>>

We solve the first challenge by assuming that the share of detected cases would have 
remained at the level it reached before Christmas if rapid tests had not become 
available. While this is only an approximation to reality, changes in the share of 
detected cases that would have happened without rapid tests are very likely to be small 
compared to the changes caused by rapid tests. In addition, the number of PCR tests per 
1000 remains in the same 1.5 to 2.5 window without a visible trend over our estimation 
period \citep{owid_n_pcr_tests} which is in line with less than 0.08\% of the 
population receiving a positive rapid test on any given day in our model.

@@

In contrast to PCR tests, rapid tests are not perfect and can be falsely positive or
falsely negative. While the specificity of rapid tests is calibrated at 99.4\%
\citep{Bruemmer2021}, their sensitivity strongly depends on the timing of the rapid test
relative to the start of infectiousness \citep{Smith2021}. Before the onset of
infectiousness the sensitivity is very low (35\%). On the first day of infectiousness it
is much higher (88\%) but still lower than during the remaining infectious period (92\%).
After infectiousness stops, the sensitivity drops to 50\%.
